dbRDA analysis

### 2017-06-29 doc/RMD/RDA-analysis.Rmd
reduce arrows in rda analysis

```{r resultplot, fig.width = 5, fig.height = 5}
set.seed(99)
plot_dbrda(cap11cc) + 
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
FILE <- file.path(PROJHOME, "results", "figures", "publication", "Figure7Z.pdf")
ggsave(filename = FILE, width = 88, height = 88, units = "mm", scale = 1.5)
plot_dbrda(cap16cc) +
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
```

>>>>

```{r resultplot, fig.width = 5, fig.height = 5}
set.seed(999)
plot_dbrda(cap11cc, arrows = 5) + 
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
FILE <- file.path(PROJHOME, "results", "figures", "publication", "Figure7Z.pdf")
ggsave(filename = FILE, width = 88, height = 88, units = "mm", scale = 1.5)
plot_dbrda(cap16cc, arrows = 10) +
  theme_classic(base_size = 16, base_family = "Helvetica") + 
  theme(axis.text = element_text(color = "black")) +
  theme(aspect.ratio = 1)
```
